`flippant` -- An `R` package for the automated analysis of dithionite scramblase

### 2015-09-24 inst/manuscript/manuscript.rmd
Keep on editing;

##Summary

##Availability and Implementation

@@

##Supplementary Information

@@

#Installation
`flippant` has been integrated into the `bioconductor` collection of tools for 
biomedical data analysis [@huber_orchestrating_2015] and is thus install- and
loadable as follows from within a functional `R` environment:
```{r, eval = FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite(pkgs = "flippant")
library(flippant)
```
The package depends on the following packaged extensions to `R` base 
functionality, which are automatically satisfied on installation: 
`r flippant_dependencies`.

>>>>

@@

@@

#Availablility and Implementation
`flippant` has been implemented in `R` [@r_core_team_r:_2015] and integrated 
into the `bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install- and loadable as follows from 
within a functional `R` environment:
```{r, eval = FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite(pkgs = "flippant")
library(flippant)
```
The package depends on the following packaged extensions to `R` base 
functionality, which are automatically satisfied on installation: 
`r flippant_dependencies`.
